---
title: "Assignment week 05"
author: "Deni Hodzic"
output: html_document
date: '2022-03-25'
---

```{r}
suppressPackageStartupMessages({
  library(AnnotationHub)
  library(ensembldb)
  library(GenomicRanges)
  library(epiwraps)
  library(rtracklayer)
  library(ggplot2)
})
ah <- AnnotationHub(localHub=TRUE)
ensdb <- ah[["AH89211"]]
```

## Downloading the data

Downloading peaks and signals for in Bruce mESC

```{r, eval=FALSE}
dir.create("peaks")
dir.create("tracks")
options(timeout=1800)

# H3K27me3
download.file("https://www.encodeproject.org/files/ENCFF008XKX/@@download/ENCFF008XKX.bed.gz", "peaks/H3K27me3.bed.gz")
download.file("https://www.encodeproject.org/files/ENCFF160FEV/@@download/ENCFF160FEV.bigWig", "tracks/H3K27me3.bw")

# H3K4me3
download.file("https://www.encodeproject.org/files/ENCFF247GVM/@@download/ENCFF247GVM.bed.gz", "peaks/H3K4me3.bed.gz")
download.file("https://www.encodeproject.org/files/ENCFF611GSQ/@@download/ENCFF611GSQ.bigWig", "tracks/H3K4me3.bw")
```


## Reading in the data

```{r}
k4me3 <- import("peaks/H3K4me3.bed.gz", format="NarrowPeak")
k27me3 <- import("peaks/H3K27me3.bed.gz", format="NarrowPeak")
```


## Visualizing the p300 peaks

```{r}
sum(overlapsAny(k4me3, k27me3, ))
```


Result: 3219 Overlaps between k4me3 and k27me3 -> there are 3219 bivalent regions.



## Overlaps


```{r}
listOfRegions <- list(k4me3=k4me3, k27me3=k27me3)
#regionOverlaps(listOfRegions)
regionUpset(listOfRegions)
```

Result: The graph shows 2746 overlaps between the two of them.

2) Download smooth muscle cell peaks (for H3K27me3, H3K4me3)

```{r, eval=FALSE}
download.file("https://www.encodeproject.org/files/ENCFF369AEO/@@download/ENCFF369AEO.bed.gz", "peaks/smoothH3K27me3.bed.gz")
download.file("https://www.encodeproject.org/files/ENCFF965WTD/@@download/ENCFF965WTD.bed.gz", "peaks/smoothH3K4me3.bed.gz")
```
# Reading in the data

```{r}
smoothk27me3 <- import("peaks/smoothH3K27me3.bed.gz", format = "NarrowPeak")
smoothk4me3 <- import("peaks/smoothH3K4me3.bed.gz", format = "NarrowPeak")
```


## Overlaps of mESCs and k27me3 
```{r}
sum(overlapsAny(k27me3, smoothk27me3))
```
Result: Shows 232 overlaps

## Overlaps of mESCs and k4me3 
```{r}
sum(overlapsAny(k4me3, smoothk4me3))
```
Result: Shows 1542 overlaps

## Overlaps of all of them
```{r}
smoothListofRegions <- list(k4me3=k4me3, k27me3=k27me3, smoothk27me3=smoothk27me3, smoothk4me3=smoothk4me3)
#Create a heatmap for this
#Question: why isn't the yellow and the orange field the same?
regionOverlaps(smoothListofRegions)
#Create a histogram for this
#Question: why isn't this number for the overlaps of k27me3 and k4me3 the same as when doing a regionUpset with only those 2?
regionUpset(smoothListofRegions)
```
Estimated time for completion: 3h